\documentclass{article}
\usepackage{amsmath, bm, enumerate, multicol, pgfplots, sfmath, tcolorbox}
\pgfplotsset{compat = newest}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[top=0.5in, right=1in, bottom=0.5in, left=1in]{geometry}
\pagestyle{empty}
\raggedright
\everymath{\displaystyle}

\newcounter{example}[section]
\newenvironment{example}[1][]{\refstepcounter{example}\par\medskip
   {\color{red}\textbf{Example~\theexample. #1}}}{\medskip}

\begin{document}

\section*{Adding and Subtracting Radical Expressions}

\begin{tcolorbox}[colframe=orange!70!white, coltitle=black, title=\textbf{Summary}]
\begin{enumerate}
    \item We can add or subtract like radicals just as we can add or subtract like terms.
\end{enumerate}
\end{tcolorbox}
\bigskip 

Just like we can add $2x + 3x$ to get $5x$, we can also add like radical expressions together.   \newline\\

\begin{tcolorbox}[colframe=blue!70!white, colback = white, coltitle=white, title=\textbf{Like Radicals}]
Radicals with the same root and the same radicand.
\end{tcolorbox}
\bigskip 

\begin{center}
\begin{tabular}{l|c}
Like Radicals   &   Not Like Radicals \\ \hline \\[2pt]
$2\sqrt{7} + 3\sqrt{7}$ &   $2\sqrt{7} + 3\sqrt[3]{7}$ (Different roots)  \\[0.25in]
$5\sqrt[3]{10} - 9\sqrt[3]{10}$ & $8\sqrt{10} - 3\sqrt{6}$ (Different radicands)   \\[5pt]
\end{tabular}
\end{center}
\bigskip 

\begin{example}
Add or subtract each. Assume all variables represent positive real numbers.
\begin{multicols}{3}
\begin{enumerate}[(a)]
    \item $4\sqrt{11} + 8\sqrt{11}$
    \item $5\sqrt[3]{3x} - 7\sqrt[3]{3x}$
    \item $4\sqrt{5} + 4\sqrt[3]{5}$
\end{enumerate}
\end{multicols}
\end{example}

\newpage 

Sometimes you have to simplify before you can combine like radicals.

\begin{example}
Add or subtract each. Assume all variables represent positive real numbers.
\begin{multicols}{2}
\begin{enumerate}[(a)]
    \item $\sqrt{20} + 2\sqrt{45}$
    \item $\sqrt[3]{54} - 5\sqrt[3]{16} + \sqrt[3]{2}$
\end{enumerate}
\end{multicols}
\vfill 
\begin{multicols}{2}
\begin{enumerate}[(a)]  \setcounter{enumi}{2}
    \item $\sqrt{27x}-2\sqrt{9x}+\sqrt{72x}$
    \item $\sqrt[3]{48x^4} + \sqrt[3]{6x^4}$
\end{enumerate}
\end{multicols}
\end{example}
\vfill 

\end{document}