\documentclass{article}
\usepackage{amsmath, amssymb, bm, tikz, mathtools, tcolorbox, array, sfmath, enumerate, multicol, pgfplots}
\renewcommand{\familydefault}{\sfdefault}
\pgfplotsset{compat=newest}
\usetikzlibrary{arrows.meta}
\everymath{\displaystyle}
\tikzset{>=stealth}
\tikzstyle{input} = [circle, text centered, radius = 1cm, draw = black]
\tikzstyle{function} = [rectangle, text centered, minimum width = 2cm, minimum height = 1cm, draw = black]
\usepackage[top = 0.25in, bottom = 0.25in, left = 1in, right = 1in]{geometry}
\pagestyle{empty}
\raggedright

\newcounter{example}[section]
\newenvironment{example}[1][]{\refstepcounter{example}\par\medskip
   {\color{red}\textbf{Example~\theexample. #1}}}{\medskip}

\begin{document}

\section*{Multiplying and Dividing Rational Expressions}

\begin{tcolorbox}[colframe=orange!70!white, coltitle=black, title=\textbf{Summary}]
\begin{enumerate}
    \item Factor and then divide out common factors.
    \item Multiply numerators and multiply denominators.
    \item When dividing fractions, multiply by the reciprocal of the second fraction.
\end{enumerate}
\end{tcolorbox}
\bigskip 

To multiply rational expressions:
\begin{enumerate}
    \item Factor all numerators \& denominators completely.
    \item Divide out common factors.
    \item Multiply the results.
\end{enumerate}
\bigskip 

\begin{example}
Simplify each.
\begin{enumerate}[(a)]
\begin{multicols}{2}
    \item $\frac{x+3}{x-4} \cdot \frac{x^2-2x-8}{x^2-9}$
    \item $\frac{8x+32}{x-7} \cdot \frac{x^2-4x-21}{4x^2-64}$
\end{multicols}
\vfill 
\begin{multicols}{2}
    \item $\frac{5x+5}{7x-7x^2} \cdot \frac{2x^2+x-3}{4x^2-9}$
    \item $\frac{4x+8}{6x-3x^2} \cdot \frac{3x^2-4x-4}{9x^2-4}$
\end{multicols}
\end{enumerate}
\end{example}

\vfill 
\newpage 

When dividing rational expressions, multiply by the first expression by the \emph{reciprocal} of the second expression.
\bigskip 

\begin{example}
Simplify each.
\begin{enumerate}[(a)]
\begin{multicols}{2}
    \item $\frac{4x^2-25}{2} \div \frac{2x+5}{14}$
    \item $(9x^2-49) \div \frac{3x-7}{9}$
\end{multicols}
\vfill 
\begin{multicols}{2}
    \item $\frac{x^2+3x-10}{2x} \div \frac{x^2-5x+6}{x^2-3x}$
    \item $\frac{x^2-x-12}{5x} \div \frac{x^2-10x+24}{x^2-6x}$
\end{multicols}
\end{enumerate}
\end{example}

\vfill 

\end{document}
